A hierarchical failure-time model for observational data exhibiting infant-mortality and wearout failure modes

### 2017-10-19 paper/aosgflp.tex
Small edits, months correction

We will use an alternative parameterization
where $\alpha$ is replaced by the $p$ quantile $t_{p}=\alpha \left
[-\log(1-p)\right ]^{\sigma}$. Replacing $\alpha$ in (1) with the
$\alpha=t_{p}/[-\log(1-p)]^{\sigma}$ gives
\begin{align*}
\nonumber
\Pr(T \leq t|t_{p},\sigma ) = F(t|t_{p},\sigma)&=1-
\exp \left [-\left (\frac{t}{t_{p}/[-\log(1-p)]^{\sigma}} \right )^{1/ \sigma}
\right ]\\
\label{equation:reparameterized.weibull.cdf}
&=1 - \exp\left[\log(1-p)\left(\frac{t}{t_{p}}\right)^{1/\sigma}\right], \quad t > 0.
\end{align*}
There are two important reasons for using this parameterization.
\begin{itemize}
\item
Especially with a high-reliability product, it will be easier to
elicit prior information about a quantile  ($t_p$) in the lower tail of the
distribution than it will be to elicit prior information about
$\alpha$. There is, however, generally available
information the shape parameter $\sigma$ for a given failure
mechanism (e.g., if the failure is due to a wearout mechanism, the
it is known that $\sigma<1$). 
\item
Because of heavy censoring in reliability field data, the parameter
estimates of the $\mu$ and $\sigma$ parameters will generally be
highly correlated and thus specification of independent marginal
prior distributions would be be inappropriate. On the other hand,
estimates of $t_{p}$ and $\sigma$, for some appropriately chosen
value of $p$, will be approximately independent, allowing the easier
elicitation and specification of independent marginal prior
distributions. For example, if a typical field data set has 10\%
failing, then choosing $t_{0.05}$ would 
work well.
\end{itemize}

@@

When eliciting prior distribution information it is much easier to ask about recognizable characteristics of a distribution instead of the parameters of the distribution.  Following the approach used in \cite[Section 15.2.2]{intervals} we will use diagonal braces ($\langle.,.\rangle$) to refer to $95$ percent central probability intervals, rather than the standard model parameters when specifying prior distributions.  Using this convention the prior distributions used in our analyses are
%$$t_{0.5,1} \sim \op{Lognormal}(8,4), \quad t_{0.2,2} \sim \op{Lognormal}(10,4)$$
$$t_{0.5,1} \sim \op{Lognormal} \langle 1.7,7.6\times 10^6 \rangle,\quad
t_{0.2,2} \sim \op{Lognormal}\langle 8.6, 5.6\times 10^7 \rangle$$
$$\mbox{logit}^{-1}\pi \sim \op{Logitnormal}\langle 1.0\times 10^{-3}, 7.1\times 10^{-1} \rangle,\quad
\sigma_1, \sigma_2 \stackrel{ind.}{\sim} \op{Lognormal}\langle 7.4 \times 10 ^{-3} ,1.3 \times 10^2 \rangle. $$
%\quad \sigma_2 \sim \op{Lognormal}\langle 7.4 \times 10 ^{-3} ,1.3 \times 10^2  \rangle $$

@@

We can also compare posterior estimates of time to failure under Models 1-4 for each drive-model individually.  For these comparisons, we calculate, pointwise, the posterior median of the proportion failing over a grid. That is, for every model, and for a fixed set, $\tilde{t}=\{\tilde{t}_1,\ldots,\tilde{t}_M\}$, we compute 
\begin{equation}
\label{pointwise-medians}
\op{median}\left\{\op{GLFP}\left(\tilde{t}_m|\pi_{g}^{(s)},t_{p_{1}g}^{(s)},\sigma_{1g}^{(s)},t_{p_{2}g}^{(s)},\sigma_{2g}^{(s)}\right);s=1,\ldots,S \right\},
\end{equation}
where $\theta^{(s)}$ is the $s^{th}$ posterior sample from $p(\theta|y)$.
%Unlike maximum likelihood, by including the hyperparameters in the probability model, there is a data-dependent penalization that results in shrinkage toward a common overall model.

@@

A possible explanation for the discrepancy shown in Figure 7 is that
the units of Drive-model 4 were introduced into the field over a
period of 5 months. Manufactures of hard drives (and most other
products) often make changes to the product design over time to
either improve reliability or to reduce cost. Such changes will
sometimes have an important effect on the products failure-time
distribution, invalidating one of our important assumptions that
failure-time distribution for a drive-model does not depend on the
date of manufacture.

@@

\section{Definition of global average for Model 4}
\label{global-avg}
In Section \ref{model-assessment}, to illustrate the concept of shrinkage in our hierarchical model, we refer to a `global average' which represents an average GLFP cdf for the entire population, $\op{H}\left(\cdot|\bar{\pi},\mu_1,\sigma_1,\bar{\mu}_2,\bar{\sigma}_2\right)$. Since $\mu_1$ and $\sigma_1$ are shared across drive-models, these can already be interpreted as `global'. For the parameters that vary across drive models, we select values corresponding to the medians of the hierarchical distributions (\ref{eq:hier-model}) conditional on the hyperparameters. In particular, setting
$$\bar{\pi}=\op{logit}^{-1}(\eta_{\pi}),\;\bar{\mu}_2=\eta_{t_2} - m_{\sigma_2}\Phi^{-1}(.2) \mbox{ and } \bar{\sigma}_2= m_{\sigma_2}.$$
Let $F(\cdot|a,b),\;F^{-1}(\cdot|a,b)$ denote the cdf and inverse cdf, respectively, for a log-normal distribution with log-location parameter $a$ and log-scale parameter $b$. Then
$$m_{\sigma_2}=F^{-1}[0.5 \cdot F(1|\eta_{\sigma_2},\tau_{\sigma_2})|\eta_{\sigma_2}, \tau_{\sigma_2}],$$
which is the median of a log-normal distribution with parameters $\eta_{\sigma_2}$, and $\tau_{\sigma_2}$, truncated to the interval $(0, 1)$.

>>>>

We will use an alternative parameterization
where $\alpha$ is replaced by the $p$ quantile $t_{p}=\alpha \left
[-\log(1-p)\right ]^{\sigma}$. Replacing $\alpha$ in (1) with the
$\alpha=t_{p}/[-\log(1-p)]^{\sigma}$ gives
\begin{align*}
\nonumber
\Pr(T \leq t|t_{p},\sigma ) = F(t|t_{p},\sigma)&=1-
\exp \left [-\left (\frac{t}{t_{p}/[-\log(1-p)]^{\sigma}} \right )^{1/ \sigma}
\right ]\\
\label{equation:reparameterized.weibull.cdf}
&=1 - \exp\left[\log(1-p)\left(\frac{t}{t_{p}}\right)^{1/\sigma}\right], \quad t > 0.
\end{align*}
There are two important reasons for using this parameterization.
\begin{itemize}
\item
Especially with a high-reliability product, it will be easier to
elicit prior information about a quantile  ($t_p$) in the lower tail of the
distribution than it will be to elicit prior information about
$\alpha$. There is, however, generally available
information the shape parameter $\sigma$ for a given failure
mechanism (e.g., if the failure is due to a wearout mechanism, then
it is known that $\sigma<1$). 
\item
Because of heavy censoring in reliability field data, the parameter
estimates of the $\mu$ and $\sigma$ parameters will generally be
highly correlated and thus specification of independent marginal
prior distributions would be be inappropriate. On the other hand,
estimates of $t_{p}$ and $\sigma$, for some appropriately chosen
value of $p$, will be approximately independent, allowing the easier
elicitation and specification of independent marginal prior
distributions. For example, if a typical field data set has 10\%
failing, then choosing $t_{0.05}$ would 
work well.
\end{itemize}

@@

When eliciting prior distribution information it is much easier to ask about recognizable characteristics of a distribution instead of the parameters of the distribution.  Following the approach used in \cite[Section 15.2.2]{intervals} we will use diagonal braces ($\langle.,.\rangle$) to refer to $95$ percent central probability intervals, rather than the standard model parameters when specifying prior distributions.  Using this convention the prior distributions used in our analyses are
%$$t_{0.5,1} \sim \op{Lognormal}(8,4), \quad t_{0.2,2} \sim \op{Lognormal}(10,4)$$
$$t_{0.5,1} \sim \op{Log-normal} \langle 1.7,7.6\times 10^6 \rangle,\quad
t_{0.2,2} \sim \op{Log-normal}\langle 8.6, 5.6\times 10^7 \rangle$$
$$\pi \sim \op{Logit-normal}\langle 1.0\times 10^{-3}, 7.1\times 10^{-1} \rangle,\quad
\sigma_1, \sigma_2 \stackrel{ind.}{\sim} \op{Log-normal}\langle 7.4 \times 10 ^{-3} ,1.3 \times 10^2 \rangle. $$
%\quad \sigma_2 \sim \op{Lognormal}\langle 7.4 \times 10 ^{-3} ,1.3 \times 10^2  \rangle $$

@@

We can also compare posterior estimates of time to failure under Models 1-4 for each drive-model individually.  For these comparisons, we calculate, pointwise, the posterior median of the proportion failing over a grid. That is, for every model, and for a fixed set, $\tilde{t}=\{\tilde{t}_1,\ldots,\tilde{t}_M\}$, we compute 
\begin{equation}
\label{pointwise-medians}
\op{median}\left\{\op{H}\left(\tilde{t}_m|\pi_{g}^{(s)},t_{p_{1}g}^{(s)},\sigma_{1g}^{(s)},t_{p_{2}g}^{(s)},\sigma_{2g}^{(s)}\right);s=1,\ldots,S \right\},
\end{equation}
where $\theta^{(s)}$ is the $s^{th}$ posterior sample from $p(\theta|y)$.
%Unlike maximum likelihood, by including the hyperparameters in the probability model, there is a data-dependent penalization that results in shrinkage toward a common overall model.

@@

A possible explanation for the discrepancy shown in Figure 7 is that
the units of Drive-model 4 were introduced into the field over a
period of 22 months. Manufactures of hard drives (and most other
products) often make changes to the product design over time to
either improve reliability or to reduce cost. Such changes will
sometimes have an important effect on the products failure-time
distribution, invalidating one of our important assumptions that
failure-time distribution for a drive-model does not depend on the
date of manufacture.

@@

\section{Definition of global average for Model 4}
\label{global-avg}
In Section \ref{model-assessment}, to illustrate the concept of shrinkage in our hierarchical model, we refer to a `global average' which represents an average GLFP cdf for the entire population, $\op{H}\left(\cdot|\bar{\pi},\mu_1,\sigma_1,\bar{\mu}_2,\bar{\sigma}_2\right)$. Since $\mu_1$ and $\sigma_1$ are shared across drive-models, these can already be interpreted as `global'. For the parameters that vary across drive models, we select values corresponding to the medians of the hierarchical distributions (\ref{eq:hier-model}) conditional on the hyperparameters. In particular, we set
$$\bar{\pi}=\op{logit}^{-1}(\eta_{\pi}),\;\bar{\mu}_2=\eta_{t_2} - m_{\sigma_2}\Phi^{-1}(.2) \mbox{ and } \bar{\sigma}_2= m_{\sigma_2}.$$
Let $J(\cdot|a,b),\;J^{-1}(\cdot|a,b)$ denote the cdf and inverse cdf, respectively, for a log-normal distribution with log-location parameter $a$ and log-scale parameter $b$. Then
$$m_{\sigma_2}=J^{-1}[0.5 \cdot J(1|\eta_{\sigma_2},\tau_{\sigma_2})|\eta_{\sigma_2}, \tau_{\sigma_2}],$$
which is the median of a log-normal distribution with parameters $\eta_{\sigma_2}$, and $\tau_{\sigma_2}$, truncated to the interval $(0, 1)$.
